### 2020-05-07 experiments.tex
more python details

For Python, as with Java, many mutants we inspected for {\bf RQ5} involved deletion of a call or change in comparison operator, leading to a likely method call or access to a variable containing {\tt None}, and the generated finding reported this problem.  More Python mutants were extremely difficult to understand than for Solidity or Java, without a grasp of the larger program context, but a large number were clearly due to differences in analysis engine capabilities, since all tools aim to detect failure to guard against improper uses of {\tt None}, the Python equivalent of a Java NPE.  Again, based on a qualitative examination of many mutants, we believe the results to primarily rest on realistic faults, which some tools correctly detected and others did not.

>>>>

For Python, as with Java, many mutants we inspected for {\bf RQ5} involved deletion of a call or change in comparison operator, leading to a likely method call or access to a variable containing {\tt None}, and the generated finding reported this problem.  Another example of a possibly engine-based mutation difference is that pyflakes did a much better job than the other tools of detecting cases where a mutant caused an exception to be unwisely ignored; these accounted for more than 10\% of differentially-relevant mutants.  We assume the issue is engine-based in that while pyflakes did by far the best at this (real) problem, there were instances where another tool found the problem and it did not.  On the other hand, pyflakes, in the sample we examined, did worst at detecting mutants that removed a needed argument from a function call, another common pattern (Pylint performed best for this type of mutant).  Again, based on a qualitative examination of many mutants, we believe the results to primarily rest on realistic faults, which some tools correctly detected and others did not.
